Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying

### 2023-02-21 Outputs/Paper/paper.qmd
update paper 3

@@

## Measurements

# Discussion

## First discussion point

As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year. Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities. Reports show that 81% of Asian adults state violence against them is increasing. Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.

We conducted a study to determine if there was a correlation between the increasing anti-Asian sentiment and school bullying in the United States. To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state. Figures 2 and 3 were used to compare the search frequency of the keyword "school bullying" and the date.

```{r}
#| label: School bullying searches in top 10 states with highest asian population
#| fig-cap: School bullying searches in top 10 states with highest asian population
#| echo: false
#| warning: false

@@

Figure 2 shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population. The graph indicates that March 1st, 2018, had the highest number of searches for "school bullying" at over 400. Typically, the search frequency for "school bullying" is highest in March, and there is a significant drop in search frequency every July at approximately 150 searches when summer vacation is halfway through. In contrast, data for September and January are relatively closer to the average, ranging from 150 to 300.

```{r}
#| label: School bullying searches nationwide
#| fig-cap: School bullying searches nationwide
#| echo: false
#| warning: false

@@

Figure 3 presents data on the search frequency of the keyword "school bullying" nationally since 2016. Like Figure 2, March 1st, 2018, had the highest search frequency at 2000 nationally. On the other hand, July's search frequency was always at the lowest level, with data from 2016 to 2021 never exceeding 750. September and January have a similar level of search frequency ranging from 750 to 1500, which is closer to the overall average. In terms of trends, the search frequency with respect to date was relatively consistent in both the top ten states with the highest Asian population and nationwide. Based on our analysis, we did not find a correlation between school bullying searches and the Asian population of the state.

Upon comparing Figure 2 and Figure 3, we observed a consistent trend. Notably, the months of January and September, which mark the beginning of school, exhibit comparable search frequency levels for the keyword "school bullying." Meanwhile, March, which falls in the middle of the semester, experiences a significant surge in search frequency, as seen in both national data and the top ten states with the highest Asian population. On the other hand, July, which is in the middle of summer break, displays a considerable drop in search frequency in both graphs. Overall, the trend in search frequency with respect to date remains relatively consistent across the top ten states with the highest Asian population and the entire nation. Therefore, the comparison of these two graphs did not establish any significant correlation.

In summary, by comparing trends in two graphs, our investigation did not reveal any correlation between the Asian population of a state and the frequency of searches related to school bullying. While anti-Asian culture is still a large concern in the U.S., it does not seem to have a direct impact on school bullying. It is possible that factors like school policies, awareness campaigns, and changes in social media usage have made a positive impact on preventing discrimination and stereotyping from happening.

@@

## Weaknesses

@@

## Next steps

@@

## Bias

>>>>

## Estimand
In the study, our estimated population vary for different datasets. The population of the data used in figures 1, 2, 3, and 4 contains people who live in the top ten states with the highest Asian population. These states includes California, Florida, Hawaii, Illinois, Massachusetts, New Jersey, New York, Texas, Virginia, and Washington. (@cit3) Nationwide data includes population of all people who live in the United States.

@@

The data used in this study were pulled from reproducible package of article "Data and code for: The COVID-19 pandemic disrupted both school bullying and cyberbullying." (@cit4) According to the article, raw data were provided from Google Trends and Youth Risk Behavior Survey.

To analysis these data, R programing language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used. ggplot2 (@citeggplot2) has been used in order to produce graphic reports. The use of knitr (@citeknitr) helped us to generate tables. Lubridate (@citelubridate) are used to reformat dates.

## Measurements
All the data we used is from after 2016. In our study, bullying data includes school bullying data and cyberbullying data. We measure the intensity of bullying by number of hits in one day. In the paper, we will refer it as search frequency.

## Data Analysis

### bullying number droped after covid

### Correlation between asian population of states and school bullying numbers

We conducted a study to determine if there was a correlation between the increasing anti-Asian sentiment and school bullying in the United States. To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state. Figures 4 and 5 were used to compare the search frequency of the keyword "school bullying" and the date.

```{r}
#| label: School bullying searches in top 10 states with highest asian population
#| fig-cap: "School bullying searches in top 10 states with highest asian population"
#| echo: false
#| warning: false

@@

Figure 4  shows the frequency of the keyword "school bullying" searched online within the top ten states with the highest Asian population. The graph indicates that March 1st, 2018, had the highest number of searches for "school bullying" at over 400. Typically, the search frequency for "school bullying" is highest in March, and there is a significant drop in search frequency every July at approximately 150 searches when summer vacation is halfway through. In contrast, data for September and January are relatively closer to the average, ranging from 150 to 300.

```{r figure2}
#| label: School bullying searches nationwide
#| fig-cap: School bullying searches nationwide
#| echo: false
#| warning: false

@@

Figure 5 presents data on the search frequency of the keyword "school bullying" nationally since 2016. Like Figure 4, March 1st, 2018, had the highest search frequency at 2000 nationally. On the other hand, July's search frequency was always at the lowest level, with data from 2016 to 2021 never exceeding 750. September and January have a similar level of search frequency ranging from 750 to 1500, which is closer to the overall average. In terms of trends, the search frequency with respect to date was relatively consistent in both the top ten states with the highest Asian population and nationwide. Based on our analysis, we did not find a correlation between school bullying searches and the Asian population of the state.

Upon comparing Figure 4 and Figure 5, we observed a consistent trend. Notably, the months of January and September, which mark the beginning of school, exhibit comparable search frequency levels for the keyword "school bullying." Meanwhile, March, which falls in the middle of the semester, experiences a significant surge in search frequency, as seen in both national data and the top ten states with the highest Asian population. On the other hand, July, which is in the middle of summer break, displays a considerable drop in search frequency in both graphs. Overall, the trend in search frequency with respect to date remains relatively consistent across the top ten states with the highest Asian population and the entire nation. Therefore, the comparison of these two graphs did not establish any significant correlation.

### compare top 10 and bottom 10

# Discussion
## First discussion point

As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year. Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities. Reports show that 81% of Asian adults state violence against them is increasing. (@cit1) Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic. (@cit2)

In the previous section, our investigation did not reveal any correlation between the Asian population of a state and the frequency of searches related to school bullying by comparing trends in two graphs. While anti-Asian culture is still a large concern in the U.S., it does not seem to have a direct impact on school bullying. It is possible that factors like school policies, awareness campaigns, and changes in social media usage have made a positive impact on preventing discrimination and stereotyping from happening.

@@

# Weaknesses

@@

# Next steps

@@

# Bias
